Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-03 doc/RMD/mlg-mcg.Rmd
add new supplementary figure for #15

There are a whole buttload of MLGs for those 5 MCGs. What are the severity 
ratings for those? Again, we take take a look at these AND simultaneously query
the top 5 MLGs for this.

```{r severity, fig.width = 7, fig.height = 4}
count_group <- . %>% 
  mutate(nobs = n()) %>%  # count the number of samples/MCG
  ungroup() %>%
  arrange(desc(nobs)) # arrange by number of samples and reorder factors 
Severity <- filter(strat, MCG %in% mcgs$MCG[1:8]) %>%
  group_by(MCG) %>% 
  count_group %>%
  mutate(MCG = forcats::fct_inorder(factor(MCG), ordered = TRUE)) %>%
  mutate(MLG = ifelse(MLG %in% mlgs$MLG[1:5], paste("MLG", MLG), "Other"))

severity_plot <- ggplot(Severity, aes(x = MCG, y = Severity)) +
  geom_point(aes(fill = MLG), 
             position = position_jitter(width = 0.2),
             alpha = 0.75,
             pch = 21) +
  scale_fill_manual(values = c(viridis(5, direction = -1), NA)) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(aspect.ratio = 0.6) +
  facet_wrap(~Region, nrow = 2) +
  ylim(c(3.5, 8)) +
  labs(list(
    title = "Severity by MCG and Region",
    fill = "Multilocus Haplotype",
    subtitle = "Five most abundant multilocus genotypes shown"
  ))
severity_plot
if (!interactive())
  ggsave(severity_plot, filename = "results/figures/publication/FigureS3.pdf", width = 183, unit = "mm")
```

>>>>

There are a whole boatload of MLGs for those 8 MCGs. What are the severity 
ratings for those? Again, we take take a look at these AND simultaneously query
the top 5 MLGs for this.

```{r severity, fig.width = 7, fig.height = 4.5}
count_group <- . %>% 
  mutate(nobs = n()) %>%  # count the number of samples/MCG
  ungroup() %>%
  arrange(desc(nobs)) # arrange by number of samples and reorder factors 
Severity <- filter(strat, MCG %in% mcgs$MCG[1:8]) %>%
  group_by(MCG) %>% 
  count_group %>%
  mutate(MCG = forcats::fct_inorder(factor(MCG), ordered = TRUE)) %>%
  mutate(MLG = ifelse(MLG %in% mlgs$MLG[1:5], paste("MLH", MLG), "Other"))

severity_plot <- ggplot(Severity, aes(x = MCG, y = Severity)) +
  geom_point(aes(fill = MLG), 
             position = position_jitter(width = 0.2),
             alpha = 0.75,
             pch = 21) +
  scale_fill_manual(values = c(viridis(5, direction = -1), NA)) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom") +
  theme(aspect.ratio = 0.5) +
  facet_wrap(~Region, nrow = 3) +
  ylim(c(1, 9)) +
  labs(list(
    y = "Aggressiveness",
    #title = "Aggressiveness by MCG and Region",
    fill = "Multilocus Haplotype"
    #subtitle = "Five most abundant multilocus haplotypes shown"
  )) +
  theme(legend.position = c(0.75, 0.1)) +
  theme(legend.title.align = 0.5) +
  guides(fill = guide_legend(nrow = 2))
severity_plot
if (!interactive())
  ggsave(severity_plot, filename = "results/figures/publication/RMM-aggressiveness.pdf", width = 183, height = 183*(4.5/7), unit = "mm")
```

### 2017-11-03 doc/manuscript/manuscript.Rmd
add new supplementary figure for #15

Agressiveness of the isolates ranged from `r paste(range(other(dat11)$meta$Severity), collapse = " to ")` with a mean of `r signif(mean(other(dat11)$meta$Severity), 3)` and median of `r signif(median(other(dat11)$meta$Severity), 3)`.
The group mean averages were `r sprintf("%0.2f, %0.2f, and %0.2f", Raggmean, Maggmean, Haggmean)` for Region, MCG, and MLH, respectively.
Our assessment of aggressiveness in association with Region showed a significant effect (*P* < 1.00e^-4^), with means that ranged from 5.8 (MN) to 4.0 (CA) (Fig. \@ref(aggressiveness-boxplot), Table \@ref(tab:region-aggressiveness)). 
MCGs also showed a significant effect (*P* < 0.001), with means that ranged from 6.0 ('MCG 44') to 4.6 ('MCG 49'; Table \@ref(tab:MCG-aggressiveness)).
We additionally found a significant effect for MLHs (*P* < 0.001), with means that ranged from 6.0 ('MLH 78') to 4.3 ('MLH 140') (Table \@ref(tab:MLG-aggressiveness)).

@@

>>>>

Agressiveness of the isolates ranged from `r paste(range(other(dat11)$meta$Severity), collapse = " to ")` with a mean of `r signif(mean(other(dat11)$meta$Severity), 3)` and median of `r signif(median(other(dat11)$meta$Severity), 3)`.
The group mean averages were `r sprintf("%0.2f, %0.2f, and %0.2f", Raggmean, Maggmean, Haggmean)` for Region, MCG, and MLH, respectively.
A strip plot showing the distribution of severity across these three variables simultaneously can be seen in figure \@ref(mcg-mlh-region-aggressiveness).
Our assessment of aggressiveness in association with Region showed a significant effect (*P* < 1.00e^-4^), with means that ranged from 5.8 (MN) to 4.0 (CA) (Fig. \@ref(aggressiveness-boxplot), Table \@ref(tab:region-aggressiveness)). 
MCGs also showed a significant effect (*P* < 0.001), with means that ranged from 6.0 ('MCG 44') to 4.6 ('MCG 49'; Table \@ref(tab:MCG-aggressiveness)).
We additionally found a significant effect for MLHs (*P* < 0.001), with means that ranged from 6.0 ('MLH 78') to 4.3 ('MLH 140') (Table \@ref(tab:MLG-aggressiveness)).

@@

<!-- Strip plot of Aggressiveness for MLH, MCG, and Region -->

![
Strip plot of aggressiveness for the eight most abundant MCGs partitioned by region.
Filled circles indicate one of the five most abundant MLHs and open circles indicate a MLH of lesser abundance.
](../../results/figures/publication/RMM-aggressiveness.pdf){#mcg-mlh-region-aggressiveness width=100%}
